Bitmap Indexing for Fast Analysis of Large Datasets

### 2016-03-28 ms/ms.tex
Enhanced description of metrics in tests

%---------------------------------------------------------------------------------
%---------------------------------------------------------------------------------
% TESTS
\section{Tests}\label{S:tests}
The utility of using Morton index bitmaps for mapping files to decrease query times was tested on artificial datasets containing $1024^3$ points in three dimensions, distributed between 512 files. For each test a Morton index bitmap was constructed for the dataset and used to identify files touched by cube shaped three-dimensional selectors. The performance was then assessed in terms of the number of files touched and the time required to identify the files touched. This was done for varying index orders (\S\ref{SS:test_order}), selector sizes (\S\ref{SS:test_size}), and partitions of the domain across the files (\S\ref{SS:test_decomp}).

>>>>

%---------------------------------------------------------------------------------
%---------------------------------------------------------------------------------
% TESTS
\section{Tests}\label{S:tests}
The utility of using Morton index bitmaps for mapping files to decrease query times was tested on artificial datasets containing $1024^3$ points in three dimensions, distributed between 512 files. For each test a Morton index bitmap was constructed for the dataset and used to identify files touched by cube shaped three-dimensional selectors. The performance was then assessed in terms of the number of files touched and the time required to identify the files touched. If fewer files are touched, fewer files will need to be loaded during analysis of a selected region and the overall fraction of time spent on I/O will be lower. If less time is required to identify the files touched by a given selector, more selections can be made using the same computational resources. This was done for varying index orders (\S\ref{SS:test_order}), selector sizes (\S\ref{SS:test_size}), and partitions of the domain across the files (\S\ref{SS:test_decomp}).
